sWGS validation report

### 2019-08-16 Validation Report.Rmd
...

fit = models$`0.9`
lambda = performance.at.1se$`0.9`$lambda

@@

@@

if (file.exists(paste0(pred.dir, '/batch8_preds.txt'))) {
  batch8_preds = read_tsv(paste0(pred.dir, '/batch8_preds.txt'))
} else {
  segFiles = grep(paste(on$`Patient ID`,collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', 'segObj',  full.names = T, recursive = T), value=T)

@@

  write_tsv(batch8_preds, paste0(pred.dir, '/batch8_preds.txt'))
}

@@

sheets = readxl::excel_sheets(val.file)[9:12]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'P') %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% dplyr::mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

if (file.exists(paste0(pred.dir, '/oldp_preds.txt'))) {
  oldp.preds = read_tsv(paste0(pred.dir, '/oldp_preds.txt'))
} else {
  segFiles = grep(paste(oldp$`Patient ID`,collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', 'segObj',  full.names = T, recursive = T), value=T)

@@

    prr = BarrettsProgressionRisk::predictRiskFromSegments(segmented, model = fit, s = lambda, verbose = F)
    predictions(prr)
  }))
  write_tsv(oldp.preds, paste0(pred.dir, '/oldp_preds.txt'))
}

@@

if (file.exists(paste0(pred.dir, '/val_np.txt'))) {
  new.np.preds = read_tsv(paste0(pred.dir, '/val_np.txt'))
} else {
  segFiles = grep(paste(sub('\\(.*\\)','', new.np$`Patient ID`),collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', '(2|3)_segObj',  full.names = T, recursive = T), value=T)

  new.np.preds = do.call(bind_rows, lapply(segFiles, function(f) {
    print(f)
    load(f)  
    if (nrow(BarrettsProgressionRisk::sampleResiduals(segmented) %>% dplyr::filter(Pass)) <= 0) return()

    segmented$sample.info = BarrettsProgressionRisk::loadSampleInformation(info %>% filter(Sample %in% segmented$sample.info$Sample) )
    prr = BarrettsProgressionRisk::predictRiskFromSegments(segmented, model = fit, s = lambda, verbose = F)
    p = predictions(prr)
    print(p)
    return(p)
  }))
  write_tsv(new.np.preds, paste0(pred.dir, '/val_np.txt'))
}

>>>>

@@

```{r echo=F}

alpha = '0.9'
fit = models[[alpha]]
lambda = performance.at.1se[[alpha]]$lambda

@@

file = paste0(pred.dir, '/batch8_preds_alpha', alpha,'.txt')

if (file.exists(file)) {
  batch8_preds = read_tsv(file)
} else {
  segFiles = grep(paste(on$`Patient ID`,collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', 'segObj',  full.names = T, recursive = T), value=T)

@@

  write_tsv(batch8_preds, path=file)
}

@@

sheets = readxl::excel_sheets(val.file)[9:13]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'P') %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% dplyr::mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

file = paste0(pred.dir, '/oldp_preds_alpha', alpha, '.txt')
if (file.exists(file)) {
  oldp.preds = read_tsv(file)
} else {
  segFiles = grep(paste(oldp$`Patient ID`,collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', 'segObj',  full.names = T, recursive = T), value=T)

@@

    prr = BarrettsProgressionRisk::predictRiskFromSegments(segmented, model = fit, s = lambda, verbose = F)
    predictions(prr)
  }))
  write_tsv(oldp.preds, path=file)
}

@@

file = paste0(pred.dir, '/val_np_alpha', alpha, '.txt')
if (file.exists(file)) {
  new.np.preds = read_tsv(file)
} else {
  segFiles = grep(paste(sub('\\(.*\\)','', new.np$`Patient ID`),collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', '(2|3)_segObj',  full.names = T, recursive = T), value=T)

  new.np.preds = do.call(bind_rows, lapply(segFiles, function(f) {
  #  print(f)
    load(f)  
    if (nrow(BarrettsProgressionRisk::sampleResiduals(segmented) %>% dplyr::filter(Pass)) <= 0) return()

    segmented$sample.info = BarrettsProgressionRisk::loadSampleInformation(info %>% filter(Sample %in% segmented$sample.info$Sample) )
    prr = BarrettsProgressionRisk::predictRiskFromSegments(segmented, model = fit, s = lambda, verbose = F)
    p = predictions(prr)
    print(p)
    return(p)
  }))
  write_tsv(new.np.preds, path=file)
}
